Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
write a bit more of IV.A

The infrastructure defined for this scenario is described as follow:

\begin{itemize}
    \item \emph{Smartphones} are the devices used by the people to detect the distance from the others;
    \item \emph{Local PC} is the device used to show the alarm in the laboratory;
    \item \emph{Server} is the device used run the crowd algorithm and the wearable logic. 
\end{itemize}

The initial deployment of the system starts with the $\beta_{werable}$ executed in the \emph{Server},
the $\sigma_{wearable}$ and $\chi_{werable}$ executed in the \emph{Smartphones},
and all the \emph{Laboratory} components are executed in the \emph{Local PC}.
%
Given the infrastructure defined above, we simulate also a condition where the \emph{Server} is overloaded and, via pulverization,
we want to lightening the load of the \emph{Server} by moving the $\beta_{werable}$ in the \emph{Smartphones}.
%
Formally, we can write the reconfiguration event as follow: $\beta^{werable}_{server} \xrightarrow{\mathcal{E}} \beta^{werable}_{smartphone}$
where $\mathcal{E}$ represents the reconfiguration event due to the high load in the \emph{Server}.

>>>>

We use the following hosts in the scenario:
\begin{itemize}
    \item multiple \emph{Smartphones} used by the people to detect the distance from the others;
    \item a \emph{Monitor} used to show the alarm in the laboratory;
    \item a \emph{Server} used run the crowd algorithm and the wearable logic.
\end{itemize}

Initially, $\beta^{w}$ is allocated to the \emph{Server} while
$\sigma^{w}$ and $\chi^{w}$ are executed on the \emph{Smartphones},
and all the \emph{alert} components are executed in the \emph{Monitor}.
%
In the experiment,
we define a rule by which,
if the \emph{Server} is overloaded,
$\beta^{w}$ is moved to the \emph{Smartphones}
(with each smartphone running the $\beta^{w}$ corresponding to its $\sigma^{w}$).
%
During the experiment,
we launch several heavy-duty processes on the \emph{Server},
and we observe how the system reacts to the overload.

Given the infrastracture defined above, we simulate also a condition where the \emph{Server} is overloaded and, via pulverization,
we want to lighteninig the load of the \emph{Server} by moving the $\beta_{werable}$ in the \emph{Smartphones}.
%
Formally, we can write the reconfiguration event as follow: $\beta^{werable}_{server} \xrightarrow{\mathcal{E}} \beta^{werable}_{smartphone}$
where $\mathcal{E}$ represents the reconfiguration event due to the high load in the \emph{Server}.
